FourierTools.jl - Working with Fourier Space

### 2022-05-09 paper/paper.tex
Remove some lines in paper [skip ci]

    As seen from \autoref{eq:DFS}, the maximum frequency of a signal described with the DFS is $-\lfloor N/2 \rfloor / L$ (the border of the summation interval of $k = -\lfloor N/2 \rfloor$)\footnote{You might wonder why the maximum frequency in \autoref{eq:DFS2} would be at $k=N-1$. However, this frequency is not Nyquist sampled\footnote{According to the Whittaker–Nyquist–Shannon 
        theorem \cite{whittaker_e_t_1915_1428702}, \cite{Shannon1949}.} and leads to aliasing which results that those frequencies appear at lower frequencies.}. 
    For a signal (over the range $[0, L)$) with 7 elements, the frequencies in the Fourier series would be
    \begin{equation}
        f_{\{k\}} = \left[-\frac{3}{7 L} , -\frac{2}{7 L},  -\frac{1}{7L}, \frac{0}{7L}, \frac{1}{7L}, \frac{2}{7L}, \frac{3}{7L} \right]
        \label{eq:7elems}
    \end{equation}
    and for one with 6 elements
    \begin{equation}
       f_{\{k\}} = \left[-\frac{4}{8 L} ,-\frac{3}{8 L} ,-\frac{2}{8 L} ,-\frac{1}{8 L} ,\frac{0}{8 L} ,\frac{1}{8 L} ,\frac{2}{8 L} ,\frac{3}{8 L} \right].
       \label{eq:6elems}
    \end{equation}
    The highest frequency $-\frac{4}{8 L}$ in \autoref{eq:6elems} does not fulfill Nyquist sampling and thus 
    cannot be interpreted uniquely. As drawn in \autoref{fig:nyquist_sample}, comparing the solid green, red and blue curves, there are infinitely many periodic functions of one and the same coarsest frequency
     (varying in phase and amplitude) exhibiting same sampled values.
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \begin{axis}[xmin=-0.5, xmax=7, ymax=1.2, ymin=-1.2, width=8cm, height=5cm,
                xtick = {0, 3.1415, 6.283}, xticklabels={0, $L/2$, $L$}]
                    \addplot[sharp plot, domain=-1:9, color=green, samples=400] {0.2 * cos(deg(x))};
                    \addplot[sharp plot, domain=-1:9, color=blue, samples=100] {0.5 * cos(deg(x) - 66.42)};
                    \addplot[sharp plot, domain=-1:9, color=red, samples=100] {1 * cos(deg(x) - 78.46)};
                    \addplot[sharp plot, domain=-1:9, color=orange, samples=100] {0.2*cos(deg( 3 *x))};
                    \draw[] (axis cs:-1, 0) -- (axis cs:8, 0);
                    \draw[dashed] (axis cs:0, -2) -- (axis cs:0, 2);
                    \draw[dashed] (axis cs:3.1415, -2) -- (axis cs:3.1415, 2);
                    \draw[dashed] (axis cs:6.283, -2) -- (axis cs:6.283, 2);

>>>>

    As seen from \autoref{eq:DFS}, the maximum frequency of a signal described with the DFS is $-\lfloor N/2 \rfloor / L$ (the border of the summation interval of $k = -\lfloor N/2 \rfloor$)\footnote{You might wonder why the maximum frequency in \autoref{eq:DFS2} would be at $k=N-1$. However, this frequency is not Nyquist sampled\footnote{According to the Whittaker–Nyquist–Shannon 
        theorem \cite{whittaker_e_t_1915_1428702}, \cite{Shannon1949}.} and leads to aliasing which results that those frequencies appear at lower frequencies.}. 
    For a signal (over the range $[0, L)$) with 7 elements, the frequencies in the Fourier series would be
    \begin{equation}
        f_{\{k\}} = \left[-\frac{3}{7 L} , -\frac{2}{7 L},  -\frac{1}{7L}, \frac{0}{7L}, \frac{1}{7L}, \frac{2}{7L}, \frac{3}{7L} \right]
        \label{eq:7elems}
    \end{equation}
    and for one with 6 elements
    \begin{equation}
       f_{\{k\}} = \left[-\frac{4}{8 L} ,-\frac{3}{8 L} ,-\frac{2}{8 L} ,-\frac{1}{8 L} ,\frac{0}{8 L} ,\frac{1}{8 L} ,\frac{2}{8 L} ,\frac{3}{8 L} \right].
       \label{eq:6elems}
    \end{equation}
    The highest frequency $-\frac{4}{8 L}$ in \autoref{eq:6elems} does not fulfill Nyquist sampling and thus 
    cannot be interpreted uniquely. As drawn in \autoref{fig:nyquist_sample}, comparing the solid green, red and blue curves, there are infinitely many periodic functions of one and the same coarsest frequency
     (varying in phase and amplitude) exhibiting same sampled values.
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \begin{axis}[xmin=-0.5, xmax=7, ymax=1.2, ymin=-1.2, width=8cm, height=5cm,
                xtick = {0, 3.1415, 6.283}, xticklabels={0, $L/2$, $L$}]
                    %\addplot[sharp plot, domain=-1:9, color=green, samples=400] {0.2 * cos(deg(x))};
                    %\addplot[sharp plot, domain=-1:9, color=blue, samples=100] {0.5 * cos(deg(x) - 66.42)};
                    %\addplot[sharp plot, domain=-1:9, color=red, samples=100] {1 * cos(deg(x) - 78.46)};
                    %\addplot[sharp plot, domain=-1:9, color=orange, samples=100] {0.2*cos(deg( 3 *x))};
                    \draw[] (axis cs:-1, 0) -- (axis cs:8, 0);
                    \draw[dashed] (axis cs:0, -2) -- (axis cs:0, 2);
                    \draw[dashed] (axis cs:3.1415, -2) -- (axis cs:3.1415, 2);
                    \draw[dashed] (axis cs:6.283, -2) -- (axis cs:6.283, 2);
